Approximation as Differentiation notes

### 2025-02-10 notes/definitions.tex
Some clarity on Fam(C) and relationship to Grothendieck construction.

For a functor $F: C \to \Cat$, we have the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $C$ and an $I$-indexed family $X \in FI$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $C$ where $(Ff)(X) = Y$.
\end{itemize}

\noindent This is the Grothendieck construction for a functor $F: C \to \Cat$.

Define the fibred category $\Fam(C)$ over $\Set$ where:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with morphisms $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

\noindent This is the Grothendieck construction for the functor $\Fam(-,C)$.

>>>>

For a functor $F: D \to \Cat$, we have the Grothendieck construction for $F$ which is the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $D$ and an $I$-indexed family $X \in FI$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $D$ where $(Ff)(X) = Y$.
\end{itemize}

\noindent The fibred category $\Fam(C)$ over $\Set$ is the Grothendieck construction for the functor
$\Fam(-,C)$:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with morphisms $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}
